Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-08-01 src/tex/ms.tex
Update ms.tex

Estimations on $\kappa$ using Bilby with data from the the third LIGO-Virgo catalog, GWTC-3, was performed to constrain the plausible range of $\kappa$.
Bilby is a bayesian toolkit for GW analysis, which could calculate posterior of GW waveform parameters based on signals from
interferometer and priors of the parameters provided. \citep{Ashton_2019}

>>>>

Estimations on $\kappa$ using Bilby with data from the third LIGO-Virgo catalog, GWTC-3, was performed to constrain the plausible range of $\kappa$.
Bilby is a bayesian toolkit for GW analysis, which could calculate posterior of GW waveform parameters based on signals from
interferometer and priors of the parameters provided. \citep{Ashton_2019}
